Exp1 - Opt w_max and {A,phi)

### 2018-04-25 voltagebudget/analysis/paper_figures.Rmd
Update paper figs Rmd

# Shift-add cartoon

```{r, fig.width=1.2, fig.height=0.5}
t_start <- 0.2
t_stop <- 0.3

fig6 %>% 
  filter(t > t_start, t < t_stop) %>%
  ggplot(aes(x=t, ymin=-70e-3*1e3, ymax=osc*1e3)) +
  geom_ribbon(fill="red", alpha=0.5) +
  geom_line(aes(x=t, y=vm*1e3),color="black", alpha=1, size=.2) +
  geom_hline(yintercept=-55e-3*1e3, color="black", linetype="dotted", size=0.5) +
  geom_hline(yintercept=-70e-3*1e3, color="black", linetype="dotted", size=0.5) +
  labs(x="", y="") +
  theme_classic() +
  theme(axis.line=element_blank(),
      axis.text.x=element_blank(),
      axis.text.y=element_blank(),
      axis.ticks=element_blank(),
      # axis.title.x=element_blank(),
      # axis.title.y=element_blank(),
      legend.position="none",
      panel.background=element_blank(),
      panel.border=element_blank(),
      panel.grid.major=element_blank(),
      panel.grid.minor=element_blank(),
      plot.background=element_blank()) -> p1

fig7 %>% 
  filter(t > t_start, t < t_stop) %>%
  ggplot(aes(x=t, ymin=-70e-3*1e3, ymax=osc*1e3)) +
  geom_ribbon(fill="red", alpha=0.5) +
  geom_line(aes(x=t, y=vm*1e3),color="black", alpha=1, size=.2) +
  geom_hline(yintercept=-55e-3*1e3, color="black", linetype="dotted", size=0.5) +
  geom_hline(yintercept=-70e-3*1e3, color="black", linetype="dotted", size=0.5) +
  labs(x="", y="") +
  theme_classic() +
  theme(axis.line=element_blank(),
      axis.text.x=element_blank(),
      axis.text.y=element_blank(),
      axis.ticks=element_blank(),
      # axis.title.x=element_blank(),
      # axis.title.y=element_blank(),
      legend.position="none",
      panel.background=element_blank(),
      panel.border=element_blank(),
      panel.grid.major=element_blank(),
      panel.grid.minor=element_blank(),
      plot.background=element_blank()) -> p2

plot_grid <- rbind(c(1, 1, 1, 2, 2, 2))
grid.arrange(p1, p2, layout_matrix=plot_grid)
rm(p1, p2, plot_grid)
```

@@

# Bound 1 - V_osc/V_comp (f = 20)

```{r, fig.width=2.7, fig.height=2.2}
fig1 %>% 
  group_by(N) %>% 
  filter(V_osc/V_comp <= 3) %>% 
  filter(freq == 20) %>% 
  group_by(N) %>%
  mutate(V_free_initial = round(max(V_free), 3)) %>%
  filter(V_free_initial > 0) %>%
  ggplot(aes(x=V_osc/V_comp, y=errors*1e3, group=N)) +
  geom_line(size=0.5, alpha=0.2, color="grey") + 
  geom_vline(xintercept = 1, alpha=0.7, color="black", linetype="dashed") +
  geom_vline(xintercept = 0.5, alpha=0.5, color="black", linetype="dashed") +
  theme_classic() +
  geom_line(data=filter(fig2, freq==20, V_osc/V_comp <= 3), 
            aes(x=V_osc/V_comp, y=errors*1e3), 
            color="black", size=0.8) +
  labs(x=expression(V[o]/V[c]), y="Error (ms)") -> p1

@@

@@

# Bound 2 - n_spikes < (0, 1)

```{r, fig.width=2.6, fig.height=3.2}
max_N <- max(fig1$N)

fig1 %>% 
  filter(freq == 20) %>% 
  group_by(N) %>%
  mutate(V_free_initial = round(max(V_free), 3)) %>%
  filter(V_free_initial > 0) %>%
  ggplot(aes(x=V_osc/V_b, y=(variances/n_spikes)*1e3, group=N)) +
  geom_line(size=0.5, alpha=0.2, color="grey") + 
  theme_classic() +
  geom_line(data=filter(fig2, freq == 20), aes(x=V_osc/V_b, y=(variances_pop/n_spikes_pop)*1e3), 
            color="black", size=0.7, alpha=1) +
  labs(x=expression(V[o]/V[b]), y="Variance (ms)") -> p1

fig1 %>% 
  filter(freq == 20) %>% 
  group_by(N) %>%
  mutate(V_free_initial = round(max(V_free), 3)) %>%
  filter(V_free_initial > 0) %>%
  ggplot(aes(x=V_osc/V_b, y=(variances/n_spikes)*1e3, group=N, color=factor(delta_spikes))) +
  geom_line(size=0.4, alpha=0.6) + 
  scale_colour_brewer(
    palette = "Reds", guide=guide_legend(title="Spike\ncount", nrow=3)) +
  labs(x=expression(V[o]/V[b]), y="Variance (ms)") +
  theme_classic() + theme(legend.position = c(1.25, 0.8), 
        legend.background = element_rect(colour ="black"),
        legend.key.size = unit(.5, "cm"),
        legend.title = element_text(size=10),
        legend.text = element_text(size=10)) -> p2

fig1 %>% 
  filter(freq==20) %>% 
  filter(V_osc/V_comp <= 3) %>% 
  group_by(N) %>%
  mutate(V_free_initial = round(max(V_free), 3)) %>%
  filter(V_free_initial > 0) %>%
  ggplot(aes(y=V_osc/V_comp, x=factor(delta_spikes), group=delta_spikes)) +
  geom_jitter(aes(color=factor(delta_spikes)), size=0.01, alpha=0.1, width=0.2) +
  geom_boxplot(outlier.colour = NA, alpha=0.9, width=0.2) +
  scale_colour_brewer(palette = "Reds", name="Spike count") +
  geom_hline(yintercept = 1, alpha=0.7, color="black", linetype="dashed") +
  geom_hline(yintercept = 0.5, alpha=0.5, color="black", linetype="dashed") +
  theme_classic() +
  theme(legend.position = "none") +
  labs(y=expression(V[o]/V[c]), x="Spike count") + 
  coord_flip()  -> p3

# -
M = min(fig2$variances_pop/fig2$n_spikes_pop)
fig1 %>% 
  filter(freq==20) %>% 
  mutate(quantile = ntile(V_osc, 10)) %>%
  filter(quantile %in% c(1, 10)) %>% 
  ggplot(aes(x=(variances/n_spikes)*1e3, fill=factor(quantile), group=quantile)) +
  geom_density(alpha=0.6, size=0.2, color="black") +
  geom_vline(xintercept = M*1e3, color="black") +
  labs(x="Variance (ms)", y="Density (AU)") +
  scale_fill_manual(
    # values=c("#FFDED3", "#FD0D11"), 
    values=c("grey", "black"),
    name=expression("Deciles V"[o]), 
    labels=c("0 - 10%", "90 - 100%")) +
  theme_classic() +
  theme(
    legend.position="bottom", 
    legend.key.size = unit(.3, "cm"),
    legend.title = element_text(size=8),
    legend.text = element_text(size=8) ) -> p4

@@

fig1 %>%
  filter(freq==20) %>%
  group_by(N) %>%
  mutate(V_free_initial = round(max(V_free), 3)) %>%
  filter(V_free_initial > 0) %>%
  ungroup() %>% 
  group_by(N) %>% 
  sample_n_groups(8) %>% 
  ggplot(aes(x=V_osc/V_b, y=(variances/n_spikes)*1e3, color=factor(delta_spikes))) +
  geom_point(size=1, alpha=1) +
  facet_wrap(~N, nrow=8) +
  # geom_line(aes(x=V_osc/V_b, y=(variances_pop/n_spikes_pop)*1e3),
  #           color="black", size=0.7, alpha=1) +
  scale_colour_brewer(palette = "Reds", name="Spike count") +
  scale_x_continuous(breaks=c(0, 0.5, 1.0), limits = c(0, 1)) +
  scale_y_continuous(breaks=c(6, 12)) +
  labs(x=expression(V[o]/V[b]), y="Variance (ms)") +
  theme_classic() + theme(
    # legend.position="bottom",
    strip.text.x = element_text(size=0),
    strip.background = element_blank(),
    legend.position="none",
    legend.key.size = unit(.5, "cm"),
    legend.title = element_text(size=8),
    legend.text = element_text(size=8),
    # axis.line=element_blank(),
    # axis.text.x=element_blank(),
    # axis.text.y=element_blank(),
    # axis.ticks=element_blank(),
    # axis.title.x=element_blank(),
    # axis.title.y=element_blank(),
    panel.background=element_blank(),
    # panel.border=element_blank(),
    # panel.grid.major=element_blank(),
    # panel.grid.minor=element_blank(),
    plot.background=element_blank()) -> p5

fig1 %>%
  filter(freq==20) %>%
  filter(V_osc/V_comp <= 3) %>%
  group_by(N) %>%
  mutate(V_free_initial = round(max(V_free), 3)) %>%
  filter(V_free_initial > 0) %>%
  sample_n_groups(8) %>% 
  ggplot(aes(x=V_osc/V_b, y=errors*1e3, color=factor(delta_spikes))) +
  geom_point(size=1, alpha=1) +
  facet_wrap(~N, nrow=8) +
  # geom_line(aes(x=V_osc/V_b, y=errors_pop*1e3),
  #           color="black", size=0.7, alpha=1) +
  scale_colour_brewer(palette = "Reds", name="Spike count") +
  scale_x_continuous(breaks=c(0, 0.5, 1), limits = c(0, 1)) +
  scale_y_continuous(breaks=c(2, 8)) +
  labs(x=expression(V[o]/V[b]), y="Error (ms)") +
  theme_classic() + theme(
    # legend.position="bottom",
    strip.text.x = element_text(size=0),
    strip.background = element_blank(),
    legend.position="none",
    legend.key.size = unit(.5, "cm"),
    legend.title = element_text(size=8),
    legend.text = element_text(size=8),
    # axis.line=element_blank(),
    # axis.text.x=element_blank(),
    # axis.text.y=element_blank(),
    # axis.ticks=element_blank(),
    # axis.title.x=element_blank(),
    # axis.title.y=element_blank(),
    panel.background=element_blank(),
    # panel.border=element_blank(),
    # panel.grid.major=element_blank(),
    # panel.grid.minor=element_blank(),
    plot.background=element_blank()) -> p6

plot_grid <- rbind(
  c(1, 1, 1, NA, 5, 5, 6, 6),
  c(1, 1, 1, NA, 5, 5, 6, 6),
  c(1, 1, 1, NA, 5, 5, 6, 6),
  c(2, 2, 2, NA, 5, 5, 6, 6),
  c(2, 2, 2, NA, 5, 5, 6, 6),
  c(2, 2, 2, NA, 5, 5, 6, 6),
  c(3, 3, 3, NA, 5, 5, 6, 6),
  c(3, 3, 3, NA, 5, 5, 6, 6),
  c(3, 3, 3, NA, 5, 5, 6, 6),
  c(4, 4, 4, NA, NA, NA, NA, NA),
  c(4, 4, 4, NA, NA, NA, NA, NA),
  c(4, 4, 4, NA, NA, NA, NA, NA))

grid.arrange(p1, p2, p3, p4, p5, p6, layout_matrix=plot_grid)
rm(p1, p2, p3, p4, plot_grid, max_N, M)
```

@@

```{r, fig.width=0.9, fig.height=1.5}
fig12 %>%
  group_by(N) %>%
  mutate(V_free_initial = round(max(V_free), 3)) %>%
  filter(V_free_initial > 0) %>%
  filter(V_osc/V_comp <= 3) %>% 
  mutate(norm_errors = errors/max(errors)) %>% 
  ggplot(aes(x=V_osc/V_comp, y=norm_errors, group=N)) +
  geom_line(size=0.5, alpha=0.2, color="darkgrey") + 
  geom_line(data=filter(fig13, V_osc/V_comp <= 3), 
            aes(x=V_osc/V_comp, y=errors/max(errors)), 
            color="black", size=0.7) +
  geom_line(data=filter(fig2, freq==20, V_osc/V_comp <= 3), 
            aes(x=V_osc/V_comp, y=errors/max(errors)), 
            color="tan4", size=0.7, ) +
  geom_vline(xintercept = 1, alpha=0.7, color="black", linetype="dashed") +
  geom_vline(xintercept = 0.5, alpha=0.4, color="black", linetype="dashed") +
  theme_classic() +
  lims(x=c(0, 3)) +
  labs(x=expression(V[o]/V[c]), y="Norm. error") -> p1

@@

fig12 %>%
  group_by(N) %>%
  mutate(V_free_initial = round(max(V_free), 3)) %>%
  filter(V_free_initial > 0) %>%
  filter(V_osc/V_comp <= 3) %>% 
  mutate(norm_variances = variances/max(variances)) %>% 
  ggplot(aes(x=V_osc/V_comp, y=norm_variances/n_spikes, group=N)) +
  geom_line(size=0.5, alpha=0.2, color="darkgrey") + 
  geom_line(data=filter(fig13, V_osc/V_comp <= 3), 
            aes(x=V_osc/V_comp, y=(variances_pop/max(variances_pop))/n_spikes_pop), 
            color="black", size=0.8) +
  geom_line(data=filter(fig2, freq==20, V_osc/V_comp <= 3), 
            aes(x=V_osc/V_comp, y=(variances_pop/max(variances_pop))/n_spikes_pop), 
            color="tan4", size=0.7, ) +
  geom_vline(xintercept = 1, alpha=0.7, color="black", linetype="dashed") +
  geom_vline(xintercept = 0.5, alpha=0.4, color="black", linetype="dashed") +
  theme_classic() +
  lims(x=c(0, 3)) +
  labs(x=expression(V[o]/V[c]), y="Norm. variance") -> p2

@@

fig4 %>% 
  filter(alg != "coincidence") %>% 
  group_by(set, alg) %>% 
  mutate(ts = ts - min_t) -> tmp

tmp %>% 
  filter(set == "synchronized") %>%
  ggplot(aes(x=ts*1e3, y=ns, color=alg)) +
  geom_point(size=1.6, alpha=.9, shape=4) +
  geom_point(
    data=filter(tmp, set == "initial"), 
    mapping=aes(x=ts*1e3, y=ns), color="black", shape=16, alpha=0.7, size=0.5) +
  facet_grid(alg~.) +
  scale_color_brewer(palette = "Set1", guide=FALSE) +
  theme_classic() +
  labs(x="Time (ms)", y="Neuron") +
  theme(
    legend.position="none", 
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    strip.background = element_blank(),
    strip.text.y = element_text(angle = 0)) -> p1

fig3 %>% 
  filter(alg != "coincidence") %>%
  ggplot(aes(x=errors*1e3, y=obs_variances*1e3, color=alg)) +
  geom_line(size=0.8, alpha=0.8) +
  scale_color_brewer(palette = "Set1", name="Algorithm:") +
  theme_classic() +
  labs(x="Time (ms)", y="Neuron") +
  theme(legend.position="top",
    legend.key.size = unit(.5, "cm"),
    legend.title = element_text(size=10),
    legend.text = element_text(size=10),
    legend.background = element_rect(colour ="black")) +
  labs(x="Error (ms)", y="Variance (ms)") -> p2

plot_grid <- rbind(
  # c(1, 1, 1, NA, NA, NA, NA),
  c(1, 1, 1, 2, 2, 2, 2),
  c(1, 1, 1, 2, 2, 2, 2),
  c(1, 1, 1, 2, 2, 2, 2))

>>>>

@@

# V_o/V_c

```{r, fig.width=2.7, fig.height=2.2}

fig1 %>% 
  group_by(N) %>% 
  filter(V_osc/V_comp <= 3) %>% 
  filter(freq == 20) %>% 
  group_by(N) %>%
  mutate(V_free_initial = round(max(V_free), 3)) %>%
  filter(V_free_initial > 0) %>%
  ggplot(aes(x=V_osc/V_comp, y=errors*1e3, group=N)) +
  geom_line(size=0.5, alpha=0.2, color="grey") + 
  geom_vline(xintercept = 1, alpha=0.7, color="black", linetype="dashed") +
  geom_vline(xintercept = 0.5, alpha=0.5, color="black", linetype="dashed") +
  theme_classic() +
  geom_line(data=filter(fig2, freq==20, V_osc/V_comp <= 3), 
            aes(x=V_osc/V_comp, y=errors*1e3), 
            color="black", size=0.8) +
  labs(x=expression(V[o]/V[c]), y="Error (ms)") -> p1

@@

# # Norm error here
# fig1 %>% 
# filter(V_osc/V_comp < 3) %>% 
#   filter(freq == 20) %>% 
#   group_by(N, freq) %>% 
#   mutate(norm_errors = errors/max(errors)) -> tmp1
# 
# tmp1 %>% 
#   group_by(As) %>% 
#   summarise(
#     N = 0,
#     norm_errors = mean(norm_errors),
#     V_b = mean(V_b), 
#     V_osc = mean(V_osc), 
#     V_comp = mean(V_comp)) -> tmp2
# 
# tmp1 %>% 
#   group_by(N) %>% 
#   filter(V_osc/V_comp <= 3) %>% 
#   filter(freq == 20) %>%
#   group_by(N) %>%
#   mutate(V_free_initial = round(max(V_free), 3)) %>%
#   filter(V_free_initial > 0) %>%
#   ggplot(aes(x=V_osc/V_comp, y=norm_errors, group=N)) +
#   geom_line(size=0.5, alpha=0.2, color="grey") + 
#   geom_vline(xintercept = 1, alpha=0.7, color="black", linetype="dashed") +
#   geom_vline(xintercept = 0.5, alpha=0.5, color="black", linetype="dashed") +
#   theme_classic() +
#   geom_line(data=tmp2, 
#             aes(x=V_osc/V_comp, y=norm_errors), 
#             color="black", size=0.8) +
#   labs(x=expression(V[o]/V[c]), y="Norm. error") -> p2

@@

$ V_o and variance

```{r, fig.width=2.8, fig.height=3.2}
max_N <- max(fig1$N)

fig1 %>% 
  filter(freq == 20) %>% 
  group_by(N) %>%
  mutate(V_free_initial = round(max(V_free), 3)) %>%
  filter(V_free_initial > 0) %>%
  ggplot(aes(x=V_osc/V_b, y=(variances/n_spikes)*1e3, group=N, color=factor(delta_spikes))) +
  geom_line(size=0.4, alpha=0.6) + 
  scale_colour_brewer(
    palette = "Reds", guide=guide_legend(title="Spike\ncount", nrow=3)) +
  labs(x=expression(V[o]/V[b]), y="Variance (ms)") +
  theme_classic() + theme(legend.position = c(1.25, -0.8), 
        legend.background = element_rect(colour ="black"),
        legend.key.size = unit(.5, "cm"),
        legend.title = element_text(size=10),
        legend.text = element_text(size=10)) -> p1

fig1 %>% 
  filter(freq==20) %>% 
  filter(V_osc/V_comp <= 3) %>% 
  group_by(N) %>%
  mutate(V_free_initial = round(max(V_free), 3)) %>%
  filter(V_free_initial > 0) %>%
  ggplot(aes(y=V_osc/V_comp, x=factor(delta_spikes), group=delta_spikes)) +
  geom_jitter(aes(color=factor(delta_spikes)), size=0.01, alpha=0.1, width=0.2) +
  geom_boxplot(outlier.colour = NA, alpha=0.9, width=0.2) +
  scale_colour_brewer(palette = "Reds", name="Spike count") +
  geom_hline(yintercept = 1, alpha=0.7, color="black", linetype="dashed") +
  geom_hline(yintercept = 0.5, alpha=0.5, color="black", linetype="dashed") +
  theme_classic() +
  theme(legend.position = "none") +
  labs(y=expression(V[o]/V[c]), x="Spike count") + 
  coord_flip()  -> p2

# -
M = min(fig2$variances_pop/fig2$n_spikes_pop)
fig1 %>% 
  filter(freq==20) %>% 
  mutate(quantile = ntile(V_osc, 10)) %>%
  filter(quantile %in% c(1, 10)) %>% 
  ggplot(aes(x=(variances/n_spikes)*1e3, fill=factor(quantile), group=quantile)) +
  geom_density(alpha=0.6, size=0.2, color="black") +
  geom_vline(xintercept = M*1e3, color="black") +
  labs(x="Variance (ms)", y="Density (AU)") +
  scale_fill_manual(
    # values=c("#FFDED3", "#FD0D11"), 
    values=c("grey", "black"),
    name=expression("Deciles V"[o]), 
    labels=c("0 - 10%", "90 - 100%")) +
  theme_classic() +
  theme(
    legend.position="bottom", 
    legend.key.size = unit(.3, "cm"),
    legend.title = element_text(size=8),
    legend.text = element_text(size=8) ) -> p3

@@

fig1 %>%
  filter(freq==20) %>%
  group_by(N) %>%
  mutate(V_free_initial = round(max(V_free), 3)) %>%
  filter(V_free_initial > 0) %>%
  ungroup() %>% 
  group_by(N) %>% 
  sample_n_groups(8) %>% 
  ggplot(aes(x=V_osc/V_b, y=(variances/n_spikes)*1e3, color=factor(delta_spikes))) +
  geom_point(size=1, alpha=1) +
  facet_wrap(~N, nrow=8) +
  # geom_line(aes(x=V_osc/V_b, y=(variances_pop/n_spikes_pop)*1e3),
  #           color="black", size=0.7, alpha=1) +
  scale_colour_brewer(palette = "Reds", name="Spike count") +
  scale_x_continuous(breaks=c(0, 0.5, 1.0), limits = c(0, 1)) +
  scale_y_continuous(breaks=c(6, 12)) +
  labs(x=expression(V[o]/V[b]), y="Variance (ms)") +
  theme_classic() + theme(
    # legend.position="bottom",
    strip.text.x = element_text(size=0),
    strip.background = element_blank(),
    legend.position="none",
    legend.key.size = unit(.5, "cm"),
    legend.title = element_text(size=8),
    legend.text = element_text(size=8),
    # axis.line=element_blank(),
    # axis.text.x=element_blank(),
    # axis.text.y=element_blank(),
    # axis.ticks=element_blank(),
    # axis.title.x=element_blank(),
    # axis.title.y=element_blank(),
    panel.background=element_blank(),
    # panel.border=element_blank(),
    # panel.grid.major=element_blank(),
    # panel.grid.minor=element_blank(),
    plot.background=element_blank()) -> p4

fig1 %>%
  filter(freq==20) %>%
  filter(V_osc/V_comp <= 3) %>%
  group_by(N) %>%
  mutate(V_free_initial = round(max(V_free), 3)) %>%
  filter(V_free_initial > 0) %>%
  sample_n_groups(8) %>% 
  ggplot(aes(x=V_osc/V_b, y=errors*1e3, color=factor(delta_spikes))) +
  geom_point(size=1, alpha=1) +
  facet_wrap(~N, nrow=8) +
  # geom_line(aes(x=V_osc/V_b, y=errors_pop*1e3),
  #           color="black", size=0.7, alpha=1) +
  scale_colour_brewer(palette = "Reds", name="Spike count") +
  scale_x_continuous(breaks=c(0, 0.5, 1), limits = c(0, 1)) +
  scale_y_continuous(breaks=c(2, 8)) +
  labs(x=expression(V[o]/V[b]), y="Error (ms)") +
  theme_classic() + theme(
    # legend.position="bottom",
    strip.text.x = element_text(size=0),
    strip.background = element_blank(),
    legend.position="none",
    legend.key.size = unit(.5, "cm"),
    legend.title = element_text(size=8),
    legend.text = element_text(size=8),
    # axis.line=element_blank(),
    # axis.text.x=element_blank(),
    # axis.text.y=element_blank(),
    # axis.ticks=element_blank(),
    # axis.title.x=element_blank(),
    # axis.title.y=element_blank(),
    panel.background=element_blank(),
    # panel.border=element_blank(),
    # panel.grid.major=element_blank(),
    # panel.grid.minor=element_blank(),
    plot.background=element_blank()) -> p5

# Shift-add cartoon
t_start <- 0.2
t_stop <- 0.3

fig6 %>% 
  filter(t > t_start, t < t_stop) %>%
  ggplot(aes(x=t, ymin=-70e-3*1e3, ymax=osc*1e3)) +
  geom_ribbon(fill="red", alpha=0.5) +
  geom_line(aes(x=t, y=vm*1e3),color="black", alpha=1, size=.3) +
  geom_hline(yintercept=-55e-3*1e3, color="black", linetype="dotted", size=0.6) +
  geom_hline(yintercept=-70e-3*1e3, color="black", linetype="dotted", size=0.6) +
  labs(x="", y="") +
  theme_classic() +
  theme(axis.line=element_blank(),
      axis.text.x=element_blank(),
      axis.text.y=element_blank(),
      axis.ticks=element_blank(),
      # axis.title.x=element_blank(),
      # axis.title.y=element_blank(),
      legend.position="none",
      panel.background=element_blank(),
      panel.border=element_blank(),
      panel.grid.major=element_blank(),
      panel.grid.minor=element_blank(),
      plot.background=element_blank()) -> p6

fig7 %>% 
  filter(t > t_start, t < t_stop) %>%
  ggplot(aes(x=t, ymin=-70e-3*1e3, ymax=osc*1e3)) +
  geom_ribbon(fill="red", alpha=0.5) +
  geom_line(aes(x=t, y=vm*1e3),color="black", alpha=1, size=.3) +
  geom_hline(yintercept=-55e-3*1e3, color="black", linetype="dotted", size=0.6) +
  geom_hline(yintercept=-70e-3*1e3, color="black", linetype="dotted", size=0.6) +
  labs(x="", y="") +
  theme_classic() +
  theme(axis.line=element_blank(),
      axis.text.x=element_blank(),
      axis.text.y=element_blank(),
      axis.ticks=element_blank(),
      # axis.title.x=element_blank(),
      # axis.title.y=element_blank(),
      legend.position="none",
      panel.background=element_blank(),
      panel.border=element_blank(),
      panel.grid.major=element_blank(),
      panel.grid.minor=element_blank(),
      plot.background=element_blank()) -> p7

plot_grid <- rbind(
  c(1, 1, 1, NA, 4, 4, 5, 5),
  c(1, 1, 1, NA, 4, 4, 5, 5),
  c(1, 1, 1, NA, 4, 4, 5, 5),
  c(2, 2, 2, NA, 4, 4, 5, 5),
  c(2, 2, 2, NA, 4, 4, 5, 5),
  c(2, 2, 2, NA, 4, 4, 5, 5),
  c(3, 3, 3, NA, 4, 4, 5, 5),
  c(3, 3, 3, NA, NA, NA, NA, NA),
  c(3, 3, 3, NA, 6, 6, 7, 7),
  c(NA, NA, NA, NA, 6, 6, 7, 7))

  # c(3, 3, 3, NA, 4, 4, 5, 5))
  # c(3, 3, 3, NA, NA, NA, NA, NA))
  # c(3, 3, 3, NA, NA, NA, NA, NA))

grid.arrange(p1, p2, p3, p4, p5, p6, p7, layout_matrix=plot_grid)
rm(p1, p2, p3, p4, plot_grid, max_N, M)
```

@@

```{r, fig.width=0.9, fig.height=1.5}
fig12 %>%
  group_by(N) %>%
  mutate(V_free_initial = round(max(V_free), 3)) %>%
  filter(V_free_initial > 0) %>%
  filter(V_osc/V_comp <= 3) %>% 
  mutate(norm_errors = errors/max(errors)) %>% 
  ggplot(aes(x=V_osc/V_comp, y=norm_errors, group=N)) +
  geom_line(size=0.5, alpha=0.2, color="darkgrey") + 
  geom_line(data=filter(fig13, V_osc/V_comp <= 3), 
            aes(x=V_osc/V_comp, y=errors/max(errors)), 
            color="black", size=0.7) +
  geom_line(data=filter(fig2, freq==20, V_osc/V_comp <= 3), 
            aes(x=V_osc/V_comp, y=errors/max(errors)), 
            color="black", size=0.7, linetype="dotdash") +
  geom_vline(xintercept = 1, alpha=0.7, color="black", linetype="dashed") +
  geom_vline(xintercept = 0.5, alpha=0.4, color="black", linetype="dashed") +
  theme_classic() +
  lims(x=c(0, 3)) +
  labs(x=expression(V[o]/V[c]), y="Norm. error") -> p1

@@

fig12 %>%
  group_by(N) %>%
  mutate(V_free_initial = round(max(V_free), 3)) %>%
  filter(V_free_initial > 0) %>%
  filter(V_osc/V_comp <= 3) %>% 
  mutate(norm_variances = variances/max(variances)) %>% 
  ggplot(aes(x=V_osc/V_comp, y=norm_variances/n_spikes, group=N)) +
  geom_line(size=0.5, alpha=0.2, color="darkgrey") + 
  geom_line(data=filter(fig13, V_osc/V_comp <= 3), 
            aes(x=V_osc/V_comp, y=(variances_pop/max(variances_pop))/n_spikes_pop), 
            color="black", size=0.8) +
  geom_line(data=filter(fig2, freq==20, V_osc/V_comp <= 3), 
            aes(x=V_osc/V_comp, y=(variances_pop/max(variances_pop))/n_spikes_pop), 
            color="black", size=0.7, linetype="dotdash") +
  geom_vline(xintercept = 1, alpha=0.7, color="black", linetype="dashed") +
  geom_vline(xintercept = 0.5, alpha=0.4, color="black", linetype="dashed") +
  theme_classic() +
  lims(x=c(0, 3)) +
  labs(x=expression(V[o]/V[c]), y="Norm. variance") -> p2

@@

fig4 %>% 
  filter(alg != "coincidence", alg != "left") %>% 
  group_by(set, alg) %>% 
  mutate(ts = ts - min_t) -> tmp

tmp %>% 
  filter(set == "synchronized") %>%
  ggplot(aes(x=ts*1e3, y=ns, color=alg)) +
  geom_point(size=1.6, alpha=.9, shape=4) +
  geom_point(
    data=filter(tmp, set == "initial"), 
    mapping=aes(x=ts*1e3, y=ns), color="black", shape=16, alpha=0.7, size=0.5) +
  facet_grid(alg~.) +
  scale_color_brewer(palette = "Set1", guide=FALSE) +
  theme_classic() +
  labs(x="Time (ms)", y="Neuron") +
  theme(
    legend.position="none", 
    panel.border = element_rect(fill = NA, colour = "black"),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    strip.background = element_blank(),
    strip.text.y = element_text(angle = 0)) -> p1

fig3 %>% 
  filter(alg != "coincidence", alg != "left") %>%
  ggplot(aes(x=errors*1e3, y=obs_variances*1e3, color=alg)) +
  geom_line(size=0.8, alpha=0.8) +
  scale_color_brewer(palette = "Set1", name="Algorithm:") +
  theme_classic() +
  labs(x="Time (ms)", y="Neuron") +
  theme(legend.position="bottom",
    legend.key.size = unit(.5, "cm"),
    legend.title = element_text(size=10),
    legend.text = element_text(size=10),
    legend.background = element_rect(colour ="black")) +
  labs(x="Error (ms)", y="Variance (ms)") -> p2

plot_grid <- rbind(
  # c(1, 1, 1, NA, NA, NA, NA),
  c(1, 1, 1, 2, 2, 2, 2),
  c(1, 1, 1, 2, 2, 2, 2),
  c(1, 1, 1, 2, 2, 2, 2),
  c(1, 1, 1, 2, 2, 2, 2),
    c(NA, NA, NA, 2, 2, 2, 2))
  # c(1, 1, 1, 2, 2, 2, 2),
  # c(NA, NA, NA, 2, 2, 2, 2))
